\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-05-06 paper/paper/paper.tex
Implications done

\section{Preliminary Suppositions \& Implications}
Words

\subsection{Theoretical Implications}
Words

\subsection{Practical Implications}
Words

>>>>

\section{Preliminary Suppositions \& Implications}
A lot of research appears to be out of date in the field of lock security.

This research will cover Lenel/BlueDiamond's particular implementation of BLE, which to the author's knowledge has not been tested in an academic environment before.

This research will extend the Wiegand research prior by attacking newer hardware with better security features.

\subsection{Theoretical Implications}
Vulnerabilities present in BLE/RFID/Weigand will be further reaffirmed.

The failure of manufacturers to implement up to date security features in the latest version of BLE/RFID/Weigand will be known.

This research has the potential to affect the future design of locks from the Carrier/Lenel brand, in addition to removing security vulnerabilities in future revisions of the product.

If critical vulnerabilities are discovered, these vulnerabilities could potentially be used to take over many organizations that rely on Lenel/BlueDiamond technology for access control.

\subsection{Practical Implications}
This research will confirm whether Lenel’s security posture is excellent, average, or bad.

Any vulnerabilities discovered during the testing of this research will be handed over to Lenel for analysis and patching.

Lenel’s security posture will be improved due to outsider knowledge in this research not present inside Lenel.

This research will provide a baseline for future work in evaluating locks from different vendors.

If any critical vulnerabilities are discovered but not swiftly dealt with Lenel’s reputation may lower.
